Species persistence under climate and fishing

### 2014-01-23 Writing/MS.tex
Fixed broken figure links, close #8
Fixes #10

\noindent Second, we examined harvesting rules more complex than harvesting a constant proportion of the population. Whereas population persistence in the analytical model does not depend on the functional form of recruitment $f$, to perform simulations we must 
specify a recruitment function.  We chose to use a Beverton-Holt function,

@@

\noindent where $R_0$ is the intrinsic growth rate and $K$ is the carrying capacity.  In the first generation, we seeded the world with 50 individuals at a single point, as in 
\citep{ZhouKot2011}. We first allowed the population to reach equilibrium without harvesting or climate shift.  We then 
added harvesting pressure, allowed the population to again reach equilibrium, and finally added climate 
change by moving the viable patch.

We added harvesting pressure by harvesting a constant proportion of the population, in order to confirm our analytical results. 
We also extended our analytical work by evaluating the effect of a threshold harvest rule and marine protected 
areas (MPAs). With a threshold rule, we evaluated the population at each point in space to determine how 
much harvesting should occur. If the population abundance was below the designated threshold, no 
harvesting occurred. If the population exceeded the threshold, then a proportion of the `surplus' individuals 
were harvested. To implement an MPA management strategy, we used two commonly advocated approaches: 
MPAs designed to improve fisheries yields and MPAs designed for primarily for conservation. These networks 
of MPAs were introduced into our simulations by designating segments of space in which harvesting was 
forbidden (i.e.~harvesting rates were equal to $0$). The conservation MPAs had a length of twice the average 
dispersal distance and had a distance of 4 times the average dispersal distance between them. Fisheries MPAs had a length of 1/3 of the 
average dispersal distance and had a distance of 2/3 of the average dispersal distance between them.

In our simulations, we defined the critical rate of environmental shift and the critical harvest rate as model runs 
in which the total population at equilibrium was less than 0.001. Equilibrium is calculated as the mean of 300 time steps once the difference in biomass between time step $t$ and $t+1$ no greater than $0.0360515$. Equilibrium biomass and catch are defined as the total amount of fish present and harvested, respectively, at equilibrium.

@@

\begin{figure}[htbp]
\begin{subfigure}{3in}
\subcaption{\label{biomass}}
\includegraphics[width=\textwidth]{plots/eqbiomass.pdf}
\end{subfigure}
\begin{subfigure}{3in}
\subcaption{\label{rates}}
\includegraphics[width=\textwidth]{plots/critical_rates.pdf}
\end{subfigure}
%\caption{(a) The equilibrium biomass of the population as a function of the rate of environmental shift on the x-axis and the harvesting rate on the y-axis. These results are from a Gaussian dispersal kernel with parameters $L=1$, $R_0=5$, $\langle d \rangle = 0.399$.  (b) The critical harvesting rate on the y-axis as a function of the rate of environmental shift on the x-axis.  Black lines correspond to a growth rate of $R_0=3$, red to $R_0=7$, and blue to $R_0=10$.  Solid lines correspond to an average dispersal distance $\langle d \rangle =0.1$ and dashed lines correspond to an average dispersal distance $\langle d \rangle =0.25$.  These results are from an approximated Gaussian dispersal kernel with $L=1$.}
\label{baseline}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{plots/synergy.pdf}
%\caption{Positive synergy between the two stressors.  The x-axis shows the rate of environmental shift, the y-axis shows the harvesting rate, and the color indicates the loss in biomass in the doubly stressed population in excess of the sum of the losses caused by each stressor individually, $E_\text{hc}-E_\text{h}-E_\text{c}$.  These results are from an approximated Gaussian dispersal kernel with parameters $L=1$, $R_0=5$, $\langle d \rangle = 0.399$.}
\label{Synergy}
\end{center}
\end{figure}

@@

\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_sim.pdf}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_thresh.pdf}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_mpa.pdf}
\end{subfigure}
%\caption{The equilibrium biomass of the population as a function of the rate of environmental shift on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) No management.  (b) Threshold harvesting levels.  (c) MPAs.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$. }
\label{management}
\end{figure}

>>>>

\noindent Second, we examined harvesting rules more complex than harvesting a constant proportion of the population. Whereas population persistence in the analytical model does not depend on the functional form of recruitment $f$, we must specify a recruitment function to perform simulations.  We chose to use a Beverton-Holt function,

@@

\noindent where $R_0$ is the intrinsic growth rate and $K$ is the carrying capacity.  In the first generation, we seeded the world with 50 individuals at a single point, as in 
\citep{ZhouKot2011}. We first ran through 150 generations in order for the population to reach equilibrium without harvesting or climate shift.  We then 
added harvesting pressure, allowed the population to again reach equilibrium, and finally added climate 
change by moving the viable patch.

We added harvesting pressure by harvesting a constant proportion of the population, in order to confirm our analytical results. We extended our work by evaluating the effect of a threshold harvest rule and marine protected 
areas (MPAs). With a threshold rule, we evaluated the population at each point in space to determine how 
much harvesting should occur. If the population abundance was below the designated threshold, no 
harvesting occurred. If the population exceeded the threshold, then a proportion of the `surplus' individuals 
were harvested. To implement an MPA management strategy, we used two commonly advocated approaches: 
MPAs designed to improve fisheries yields and MPAs designed for primarily for conservation [REFS]. These networks 
of MPAs were introduced into our simulations by designating segments of space in which harvesting was 
forbidden (i.e.~harvesting rates were equal to $0$). The conservation MPAs had a length of 4 times the average 
dispersal distance and had a distance of 8 times the average dispersal distance between them. Fisheries MPAs had a length of 1/3 of the 
average dispersal distance and had a distance of 2/3 of the average dispersal distance between them. These distances were chosen for the following reasons: the goal of conservation-oriented MPAs is to protect source populations, ideally that are self sustaining under a static climate. Fisheries MPAs are focused on maximizing spillover of fish populations into fishable waters, thus many MPAs, each of which are smaller than the average dispersal distance, replicates this high spillover effect.

Equilibrium is calculated as the mean of 300 time steps once the difference in biomass between time step $t$ and $t+1$ was no greater than $0.1$. Equilibrium biomass and catch are defined as the total amount of fish present and harvested, respectively, at equilibrium.

@@

\begin{figure}[htbp]
\begin{subfigure}{3in}
\subcaption{\label{biomass}}
\includegraphics[width=\textwidth]{plots/eqbiomass.pdf}
\end{subfigure}
\begin{subfigure}{3in}
\subcaption{\label{rates}}
\includegraphics[width=\textwidth]{plots/critical_rates.pdf}
\end{subfigure}
\caption{
%(a) The equilibrium biomass of the population as a function of the rate of environmental shift on the x-axis and the harvesting rate on the y-axis. These results are from a Gaussian dispersal kernel with parameters $L=1$, $R_0=5$, $\langle d \rangle = 0.399$.  (b) The critical harvesting rate on the y-axis as a function of the rate of environmental shift on the x-axis.  Black lines correspond to a growth rate of $R_0=3$, red to $R_0=7$, and blue to $R_0=10$.  Solid lines correspond to an average dispersal distance $\langle d \rangle =0.1$ and dashed lines correspond to an average dispersal distance $\langle d \rangle =0.25$.  These results are from an approximated Gaussian dispersal kernel with $L=1$.
}
\label{baseline}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3in]{plots/synergy.pdf}
\caption{
%Positive synergy between the two stressors.  The x-axis shows the rate of environmental shift, the y-axis shows the harvesting rate, and the color indicates the loss in biomass in the doubly stressed population in excess of the sum of the losses caused by each stressor individually, $E_\text{hc}-E_\text{h}-E_\text{c}$.  These results are from an approximated Gaussian dispersal kernel with parameters $L=1$, $R_0=5$, $\langle d \rangle = 0.399$.
}
\label{Synergy}
\end{center}
\end{figure}

@@

\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_sim.pdf}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_thresh.pdf}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_mpa.pdf}
\end{subfigure}
\caption{
%The equilibrium biomass of the population as a function of the rate of environmental shift on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) No management.  (b) Threshold harvesting levels.  (c) MPAs.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$.
}
\label{management}
\end{figure}
